Covid-19 Fields Survey Data Protocol

### 2023-01-16 protocol/Background_and_methods_Jan_12.qmd
Updated

---
title: "Covid-19 Fields Survey Data Protocol"
author:
  - name: Ariel Mundo Ortiz
    orcid: 0000-0002-6014-4538
    email: ariel.mundo.ortiz@umontreal.ca
    affiliations:
      - name: École de santé publique - Université de Montréal
        address: 7101 Park Avenue
        city: Montreal
        state: QC
        postal-code: H3N 1X9
date: "`r Sys.Date()`"
format:
  pdf:
    link-citations: true
    number-sections: true
    include-in-header: 
      text: |
        \usepackage{placeins}
editor: visual
bibliography: bibliography/refs.bib
keep-tex: true
csl: bibliography/jama.csl
knitr:
  opts_chunk:
    dev: "ragg_png"
---

@@

- **Model 3**
    Significant values on:
- Age: None
- Race: Indigenous
- Health Region: East, Toronto
- Income: 60000-89000 CAD
- Interaction of Income and Health Region: East and 40000_59999, East and 60000_89999, Toronto and 60000-899999, East and  over_90000, North West and over_90000, North West  and under_15000
- Interaction of Age and income: A couple of low values, but none below 0.05
- Interaction of Race and Income: indigenous and 25000_39999, indigenous and over_90000, mixed and over_90000, white_caucasian and over_90000

So far, considering that the interaction of socioeconomic factors are important predictors of vaccination status, I believe the model that provides a more cohesive picture of the data is model 3 as it shows differences between race and income which could be important if we consider the types of occupations that people in certain regions do, and how these influences their vaccination status.

<!-- @tbl-model shows the odds-ratio, 95\% confidence interval, and p-value for the logistic regression model for the first dose of vaccination by age group, race, income, Health Region, and the interaction of income and Health Region.  -->

```{r, model-table}
#| message: false
#| echo: false
#| warning: false
#| fig-width: 8
#| fig-height: 8

@@

a<-modelplot(model1,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")

b<-modelplot(model2,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("Second Model")

@@

a+b+c+plot_layout(guides = 'collect')+plot_annotation(title="Fixed effects of all models")& theme(legend.position = 'bottom')

d<-modelplot(model1,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("1st Model")

@@

d+e+f+plot_layout(guides = 'collect')+plot_annotation(title="Interaction effects of all models") & theme(legend.position = 'bottom')

@@

>>>>

---
title: "Covid-19 Fields Survey Data Protocol"
author:
  - name: Ariel Mundo Ortiz
    orcid: 0000-0002-6014-4538
    email: ariel.mundo.ortiz@umontreal.ca
    affiliations:
      - name: École de santé publique - Université de Montréal
        address: 7101 Park Avenue
        city: Montreal
        state: QC
        postal-code: H3N 1X9
date: "`r Sys.Date()`"
format:
  pdf:
    link-citations: true
    number-sections: true
    include-in-header: 
      text: |
        \usepackage{placeins}
  html:
    toc: true
editor: visual
bibliography: bibliography/refs.bib
keep-tex: true
csl: bibliography/jama.csl
knitr:
  opts_chunk:
    dev: "ragg_png"
---

@@

- **Model 3**
    Significant values on:
- Age: None
- Race: Indigenous
- Health Region: East, Toronto
- Income: 60000-89000 CAD
- Interaction of Income and Health Region: East and 40000_59999, East and 60000_89999, Toronto and 60000-899999, East and  over_90000, North West and over_90000, North West  and under_15000
- Interaction of Age and income: A couple of low values, but none below 0.05
- Interaction of Race and Income: indigenous and 25000_39999, indigenous and over_90000, mixed and over_90000, white_caucasian and over_90000. A visual representation of the estimates of the models can be see below, where @fig-fixed-effects shows the odds-ratio, 95\% confidence interval for the single fixed effects of the three models. @fig-interaction-effects shows the odds ratio and 95\% confidence interval for the interaction effects of models 1 and 2, and @fig-interaction-effects-mod3 shows the interaction effects for model 3.

```{r, model-fixed-eff}
#| message: false
#| label: fig-fixed-effects
#| echo: false
#| warning: false
#| fig-width: 8
#| fig-cap: "Fixed effects of all models"
#| fig-height: 12

@@

# cm<-c('Incomeunder_15000'='Under CAD 15000',
#       'Income25000_39999'='CAD 25000-39999',
#       'Income40000_59999'='CAD 40000-59999',
#       'Income60000_89999'='CAD 60000-89999',
#       'Incomeover_90000'='Over CAD 90000',
#       'Age_group25_24'='Age 25-34',
#       'Age_group35_44'='Age 35-44',
#       'Age_group45-54'='Age 45-54',
#       'Age_group55_64'='Age 55-64',
#       'Age_group65_and_over'='Age 65 and over',
#       'Raceblack'='Black',
#       'Raceeast_asian_pacific_islander'='East Asian/Pacific Islander',
#       'Raceindigenous'="Indigenous",
#       'Racelatin_american'='Latin American',
#       'Racemixed'='mixed',
#       'Raceother'='Other',
#       'Racesouth_asian'='South Asian',
#       'Racewhite_caucasian'='White Caucasian',
#       'Health_RegionNorth East'='North East',
#       'Health_RegionNorth West'='North West',
#       'Health_RegionToronto'='Toronto',
#       'Health_RegionWest'='West',
#       
#       )

a<-modelplot(model1,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("First Model")+xlab("")

b<-modelplot(model2,coef_omit = ':')+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
  scale_color_manual(values = c("black", "red"))+ggtitle("Second Model")+xlab("")

@@

a+b+c+plot_layout(guides = 'collect',ncol=1)+plot_annotation(title="Fixed effects of all models")& theme(legend.position = 'bottom')

```{r,model-interactions}
#| message: false
#| echo: false
#| label: fig-interaction-effects
#| warning: false
#| fig-cap: "Interaction Effects of models 1 and 2"
#| fig-width: 10
#| fig-height: 10

#cm<-c('Incomeunder_15000'='Under 15000')

d<-modelplot(model1,coef_omit = "^(?!.*:)")+aes(color = ifelse(p.value < 0.05, "Significant", "Not significant"))+
  scale_color_manual(values = c("black", "red"))+ggtitle("1st Model")+xlab("")

@@

d+e+plot_layout(guides = 'collect',ncol=1)+plot_annotation(title="Interaction effects for models 1 and 2") & theme(legend.position = 'bottom')

@@

```{r,third-model}
#| message: false
#| echo: false
#| label: fig-interaction-effects-mod3
#| warning: false
#| fig-cap: "Interaction Effects of model 3"
#| fig-width: 10
#| fig-height: 15

f+plot_layout(guides = 'collect',ncol=1)+plot_annotation(title="Interaction effects for model 3") & theme(legend.position = 'bottom')

**So far, considering that the interaction of socioeconomic factors are important predictors of vaccination status, I believe the model that provides a more cohesive picture of the data is model 3 as it shows differences between race and income which could be important if we consider the types of occupations that people in certain regions do, and how these influences their vaccination status.**

### 2023-01-16 protocol/Background_and_methods_Jan_12.tex
Updated

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/15/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, breakable, sharp corners, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/16/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
